---
title: "1 Installation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{1 Installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In the following the [required software](#1-1-pre-required-software) and the 
workflow for installing the [R package kwb.pilot](#1-2-r-package-installation) 
is described.

# 1.1 Required software

- [R (>= 3.3.2)](https://cloud.r-project.org/): for the development of the R 
package **kwb.pilot** R 3.3.2 was used. However, also later R releases 
(e.g. 3.4) should be working.  

- [Rtools](https://cran.rstudio.com/bin/windows/Rtools/): required to compile R 
packages from source (Attention: the required version depends on the installed R 
version on your OS)

- [Pandoc](http://pandoc.org/installing.html): is required to convert the reports 
from plain text format (markdown) into the different formats (docx, html, pdf). 

- [Miktex](https://miktex.org/download): needs to be installed in case that **pdf** reports should be created.

For the advanced user it is further recommended to install the latest version of 
the integrated development environment (IDE) [RStudio Desktop "open source licence"](https://www.rstudio.com/products/rstudio/download2/#download). 

# 1.2 Workflow

Once all [pre-required software](#1-1-pre-required-software) is installed the R 
package installation workflow as described below can be started.

## 1.2.1 Step 1) Installation of R package "devtools" 

The R package "devtools" is required for downloading and installing the R package 
"kwb.pilot" from Github. Installation is done by executing the following 
lines of code in R or RStudio (from now on written as R(Studio)):
```r
if (!require("devtools")) {
  install.packages("devtools", repos = "https://cloud.r-project.org")
}
```

## 1.2.2 Step 2) Installation of R package "kwb.pilot"
#### 2.1) Specific release 

In case you want to install a specific release you need to specify the 
parameter "ref", which needs to be set to a valid release (check here: [releases](https://github.com/KWB-R/kwb.pilot/releases)) by running the following code in R(Studio). This tutorial at least requires release version [v.0.4.0](https://github.com/KWB-R/kwb.pilot/releases/tag/v.0.4.0)):
```r
devtools::install_github("kwb-r/kwb.pilot", 
                         ref = "v.0.4.0",
                         dependencies = TRUE)
```

***Please cite [v.0.4.0](https://github.com/KWB-R/kwb.pilot/releases/tag/v.0.4.0) 
of the R package as follows:*** [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.825030.svg)](https://doi.org/10.5281/zenodo.825030)

## 1.2.3	Step 3) Check the installation folder of the package in R(Studio) with:

By running the following code in R(Studio) you can check where the R package 
“kwb.pilot” was installed on your computer:
```{r eval = FALSE}
system.file(package = "kwb.pilot")
```

Under Windows it will be located in your personal Documents/R/win-library folder 
followed by the minor release version of the R version you are using (here: 3.3 
because the R version used for this documentation is 3.3.2): 
"C:/Users/YOUR_USERNAME/Documents/R/win-library/3.3/kwb.pilot""

## 1.2.4	Step 4) Copy site specific files

Knowing the installation folder of the “kwb.pilot” package is important, 
because two additional files, which are described in detail in the following 
sub-chapters need to be copied into the package directory, so that it is working 
properly for the Haridwar site.

### 1.2.4.1	mySQL configuration file ('.my.cnf')

The '.my.cnf' file is required to establish a connection to the mySQL database 
for querying the opera-tional data for the Haridwar site. It needs to be copied 
into the directory which is returned after run-ning the following code in R(Studio) :
```{r eval = FALSE}
system.file("shiny/haridwar", package = "kwb.pilot")
```

In this example (which is based on the R 3.3.2 release) it will be located in 
your personal documents folder under:
"C:/Users/YOUR_USERNAME/Documents/R/win-library/3.3/kwb.pilot/shiny/haridwar"

**Important note:** 
The “.my.cnf” configuration file  is not included in the R package, as it would 
provide direct access to the MySQL database of the AUTARCON company!

### 1.2.4.2	Analytics spreadsheet file ('analytics.xlsx')

The 'analytics.xlsx' file contains the analytics data (results of lab measurements) 
for the Haridwar site. It has a specific predefined structure which is expected 
by the R package and should not be changed (e.g. for all analytical parameter 
sheets to be imported the data entries are expected to start in row 70 and the 
first column is of type “DateTime”). Automatic reading of this file is not 
possible, if the structure is changed.
This file needs to be copied into the directory which is returned after running 
the following code in R(Studio):

```{r eval = FALSE}
system.file("shiny/haridwar/data", package = "kwb.pilot")
```

In this example (which is based on the R 3.3.2 release) it will be located in 
your personal documents folder under:
"C:/Users/YOUR_USERNAME/Documents/R/win-library/3.3/kwb.pilot/shiny/haridwar/data"

**Important note:**
***The “analytics.xlsx” file  is not included in the R package due to IP reasons.***
