---
title: "4 Modify"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{4 Modify}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


In the following sub-chapters three basic use cases – requiring no programming 
skills - and one advanced use case – requiring advanced R programming skills – 
are presented, in order to show how the R reporting tool can be modified.

## 4.1	Basic: update operational/analytical data
In order to use the latest operational data (from the MySQL DB of the Haridwar 
site) in the R reporting tool you need to run the following code in R(Studio):

```{r eval = FALSE}
kwb.pilot::run_app(use_live_data = TRUE)
```

If also the analytical data was updated you need to save the analytics file 
with the filename “analytics.xlsx” at the location returned by running the 
following code in R(Studio): 

```{r eval = FALSE}
system.file("shiny/haridwar/data/analytics.xlsx", package = "kwb.pilot")
```

In this example (which is based on the R 3.3.2 release) it will be located in 
your personal documents folder under:
"C:/Users/YOUR_USERNAME/Documents/R/win-library/3.3/kwb.pilot/shiny/haridwar/data/analytics.xlsx"

In order to use the latest analytics data in the R reporting tool you also need 
to run the following code in R(Studio):

```{r eval = FALSE}  
kwb.pilot::run_app(use_live_data = TRUE)
```

## 4.2	Basic: update thresholds 
The thresholds are defined in a CSV file, which is located at the location 
returned by running the following code in R(Studio): 

```{r eval = FALSE}  
system.file("shiny/haridwar/data/thesholds.csv", package = "kwb.pilot")
```

In this example (which is based on the R 3.3.2 release) it will be located in 
your personal documents folder under:
"C:/Users/YOUR_USERNAME/Documents/R/win-library/3.3/kwb.pilot/shiny/haridwar/data/thresholds.csv"

For updating e.g. the threshold for the parameter “Battery voltage” for example 
to “24”, the value in column ParameterThreshold (see Table 1) needs to be 
updated and saved. A threshold value for a parameter not defined in the table 
below can be added by typing its ParameterCode, Parameter-Name, ParameterUnit 
into a new line of “thresholds.csv”. For example all valid parameters values 
for the operational Haridwar data are defined here: 

```{r eval = FALSE}  
system.file("shiny/haridwar/data/operation_parameters.csv", package = "kwb.pilot")
```

In addition data entries for the columns ParameterThresholdComparison (i.e. >=, 
=, >=) and Pa-rameterThreshold are required, whilst ParameterThresholdSource can 
be freely defined by the user or even left blank. 
Finally the app needs to be restarted as described in Chapter 3.1.2 (in case no 
new operation/analytical data should be used) or in Chapter 3.1.1 (in case also 
new operational/analytical data should be used).


```{r eval = FALSE}  
knitr::kable(x = kwb.pilot::get_thresholds(), row.names = FALSE)
```


## 4.3	Basic: update map in site panel tab

The two maps shown in the [site panel tab](A3_4_gui_site.html) can be adapted.
During the app start the configuration file “site_info.csv”  is imported and 
used for specifying the: 

-	Coordinates: longitude and latitude 

-	Popup menu: site name, location and link

In case the user wants to change either coordinates, popup menu or both, the 
configuration file needs to be modified. Its location will be returned by 
running the following code in R(Studio):

```{r, eval=FALSE}
system.file("shiny/haridwar/data/site_info.csv", package = "kwb.pilot")
```

In this example (which is based on the R 3.3.2 release) it will be located in 
your personal documents folder under:
"C:/Users/YOUR_USERNAME/Documents/R/win-library/3.3/kwb.pilot/shiny/haridwar/data/site_info.csv"
 
## 4.4	Advanced: adapting to a different site

In general, adapting the R reporting tool to other sites is possible, as the R 
code is released using an open source [MIT licence](https://opensource.org/licenses/MIT) 
on [Github](https://github.com/KWB-R/kwb.pilot) and [Zenodo](http://doi.org/10.5281/zenodo.825030).  
However, advanced R programming techniques are required in order to adapt the 
importing, aggregation and calculations for another site. Thus it is planned 
within the AQUANES project to adapt the R reporting tool to the following five 
additional AQUANES sites:

-	Berlin-Tiefwerder (site 1)

-	Basel-Lange Erlen (site 6)

-	Agon-Countainville (site 8)

-	Berlin-Schönerlinde (site 12)

-	Packington (site 13) 
