---
title: "Pilot: MBR 4.0"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pilot: MBR 4.0}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Install R package


```{r install, eval = FALSE}

# Install latest stable version from KWB-R R-Universe
options(repos = c(
    kwbr = 'https://kwb-r.r-universe.dev',
    CRAN = 'https://cloud.r-project.org'))


install.packages('kwb.pilot')


```

## Setup Environment Variables 

For downloading the `latest` (from `Martin Systems webportal`) and `archived` (from 
`KWB Nextcloud`) `.tsv` data files  you need set the following environment variables  
**only once** as shown below. 

For doing so follow the steps below: 

1. Open `RStudio` and run `usethis::edit_r_environ()`

2. In the opened window add the required environment variables

```{r r_environment, eval = FALSE}
MBR4.0_URL = "url-to-download-pilot-plant-data"
NEXTCLOUD_URL = "https://<replace-with-dwc-cloud-url>"
NEXTCLOUD_USER = "<your-dwc-cloud-username>" # your username
NEXTCLOUD_PASSWORD = "your-nextcloud-app-password" ### see details below
```

To access the `archived` data you need to be a registered Nextcloud user with 
access to the folder `projects/MBR4.0`

For creating `<your-nextcloud-app-password>`:

* go to: https://replace-with-kwb-cloud-url/index.php/settings/user/security

* scroll down to `create new app password`

* select a name e.g. `r-script` and copy the token and replace `your-nextcloud-app-password`


3. Finally you need to restart Rstudio and proceed with the code below:


Subsequently click **Save** and restart RStudio.


## Import 

```{r import, eval = TRUE}
library(kwb.pilot)

mbr4_data_raw <- kwb.pilot::read_mbr4()
str(mbr4_data_raw)

mbr4_data_tidy <- kwb.pilot::tidy_mbr4_data(mbr4_data = mbr4_data_raw)

str(mbr4_data_tidy)

```

## Aggregate

```{r aggregate, eval = TRUE}
mbr4_data_tidy_10min <- mbr4_data_tidy %>% kwb.pilot::group_datetime(by = 600)
mbr4_data_tidy_1hour <- mbr4_data_tidy %>% kwb.pilot::group_datetime(by = 3600)
```

## Export 

### CSV files 

```{r export_data, eval = FALSE}
kwb.pilot::export_data(mbr4_data_tidy, export_dir = paths$export_dir)
kwb.pilot::export_data(mbr4_data_tidy_10min, export_dir = paths$export_dir)
kwb.pilot::export_data(mbr4_data_tidy_1hour, export_dir = paths$export_dir)
```

### Interactive HTML plots

```{r plot_data, eval = FALSE}
kwb.pilot::plot_data(mbr4_data_tidy_10min, export_dir = paths$export_dir)
kwb.pilot::plot_data(mbr4_data_tidy_1hour, export_dir = paths$export_dir)
#kwb.pilot::plot_data(mbr4_data_tidy, export_dir = paths$export_dir)
```

