---
title: "Automated report for Haridwar"
output:
  html_document:
    fig_height: 7
    fig_width: 12
    number_sections: yes
    toc: yes
  pdf_document:
    fig_height: 4.8
    fig_width: 7  
    highlight: zenburn
    number_sections: yes
    toc: yes
  word_document:
    fig_height: 5
    fig_width: 7
    toc: yes
params:
  report_aggregation: day
  report_tz: NA
  report_data: NA
  report_daterange: NA
  report_parameters_offline: NA
  report_parameters_online: NA
  report_parameters_calculated: NA
  report_add_thresholds: NA
  report_sitenames: NA
  report_timezone: NA
  run_as_standalone: yes
---

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(RMySQL)
library(ggplot2)
library(ggforce)
library(dplyr)
library(kwb.pilot)

print_items <- function(items) paste("* ", items, collapse = "  \n")

thresholds <- kwb.pilot::get_thresholds()

if (params$run_as_standalone) {
  
### Raw data
dat <- kwb.pilot::import_data_haridwar()

conf_template <- kwb.pilot::report_config_template(df = dat,
                                       temporal_aggregation = "raw", 
                                       output_timezone = "Asia/Calcutta")
kwb.pilot::report_config_to_txt(config_list = conf_template, "report_config_template.txt")

report_config_path <- file.path(getwd(), "report_config.txt")

if (file.exists(report_config_path)) {

### Import & use report configuration from "report_config.txt"
input <- kwb.pilot::report_txt_to_config(report_config_path)
  
} else {


### Set a dummy configuration in case no "report_config.txt" exists 
input <- list(report_sitenames = unique(dat$SiteName),
              report_aggregation = "day",
              report_parameters_online = unique(dat$ParameterName[dat$Source == "online"])[1],
              report_parameters_offline = unique(dat$ParameterName[dat$Source == "offline"])[6],
              report_add_thresholds = TRUE,
              report_daterange = c("2017-03-01", "2017-03-31"),
              report_timezone = "UTC")

}

### Aggregate to user defined time period

if (input$report_aggregation != "raw") {
dat <- kwb.pilot::group_datetime(dat,
                                      by = input$report_aggregation)
}


date_idx <- as.Date(dat[,"DateTime"]) >= input$report_daterange[1] & as.Date(dat[,"DateTime"]) <= input$report_daterange[2]
site_idx <- dat[,"SiteName"] %in% input$report_sitenames
para_idx <- dat[,"ParameterName"] %in% c(input$report_parameters_online, input$report_parameters_offline)
row_idx <- date_idx & site_idx & para_idx


config <- list(run_as_standalone = TRUE,
               report_tz = kwb.pilot::change_timezone(dat,tz = input$report_timezone)[date_idx,],
               report_data = kwb.pilot::change_timezone(dat[row_idx,],tz = input$report_timezone), 
               report_aggregation = input$report_aggregation,
               report_sitenames = input$report_sitenames,
               report_parameters_online = input$report_parameters_online,
               report_parameters_offline = input$report_parameters_offline,
               report_parameters_calculated = unique(kwb.pilot::calculate_operational_parameters(df = dat)$ParameterName),
               report_add_thresholds = input$report_add_thresholds,
               report_daterange = input$report_daterange,
               report_timezone = input$report_timezone
               )
} else {
  

  
 config <- list(run_as_standalone = params$run_as_standalone,
                report_tz = params$report_tz,
                report_data = params$report_data,
                report_aggregation = params$report_aggregation,
                report_sitenames = params$report_sitenames,
                report_parameters_online = params$report_parameters_online,
                report_parameters_offline = params$report_parameters_offline,
                report_parameters_calculated = params$report_parameters_calculated,
                report_add_thresholds = params$report_add_thresholds,
                report_daterange = params$report_daterange,
                report_timezone = params$report_timezone)
}

table_thresholds <- kwb.pilot::check_thresholds(df = config$report_tz)

```

# Reporting period (`r config$report_daterange[1]` -  `r config$report_daterange[2]`)

Here are the time series plots for the reporting period from `r config$report_daterange[1]` to  `r config$report_daterange[2]`
using the timezone "`r config$report_timezone`" with the following temporal aggregation 
level (i.e. median values): "`r config$report_aggregation`"


## Thresholds

The threshold satisfaction analysis is performed using the available data for 
`r nrow(table_thresholds)` parameters with pre-defined thresholds within the 
reporting period (`r config$report_daterange[1]` -  `r config$report_daterange[2]`).

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
knitr::kable(x = table_thresholds, row.names = FALSE)
```

## Online parameters

**You selected the following `r length(config$report_parameters_online)` parameter(s) for plotting:**

`r print_items(config$report_parameters_online)`

**At the following `r length(config$report_sitenames)` sampling location(s):**

`r print_items(config$report_sitenames)`

```{r, echo=FALSE, message=FALSE, warning=FALSE}

   online <- config$report_data[config$report_data[,"ParameterName"] %in% config$report_parameters_online,] %>% 
             dplyr::mutate_(label = "sprintf('%s (%s)',ParameterName, ParameterUnit)")

    for (i in seq_along(config$report_parameters_online)) {
      
    sel_par1 <- config$report_parameters_online[order(config$report_parameters_online)][i]
      
    n_measurements <- nrow(online[online[,"ParameterName"] == sel_par1,])
    
    if (n_measurements > 0) {
    
    g1 <- ggplot2::ggplot(online, ggplot2::aes_string(x = "DateTime",
                                    y = "ParameterValue",
                                    col = "SiteName")) +
      ggforce::facet_wrap_paginate(~label,
                                   nrow = 1,
                                   ncol = 1,
                                   scales = "free_y",
                                   page = i) +
      ggplot2::geom_point() +  
      ggplot2::theme_bw(base_size = 20) +
      ggplot2::theme(legend.position = "top"
                     , strip.text.x = element_text(face = "bold")
                     , legend.title = element_blank()
                     ) +
      ggplot2::labs(x = "", y = "")
    
     if (config$report_add_thresholds == TRUE & sel_par1 %in% unique(thresholds$ParameterName)) {
     sel_threshold1 <- thresholds[thresholds$ParameterName == sel_par1,]
     g1 <- g1 + ggplot2::geom_hline(yintercept =  sel_threshold1$ParameterThreshold, 
                                   linetype = "dashed")   
     } 
     print(g1) 
    }
    }
```

## Offline parameters

**You selected the following `r length(config$report_parameters_offline)` parameter(s) for plotting:**

`r print_items(config$report_parameters_offline)`

**At the following `r length(config$report_sitenames)` sampling location(s):**

`r print_items(config$report_sitenames)`

```{r, echo=FALSE, message=FALSE, warning=FALSE}

   offline <- config$report_data[config$report_data[,"ParameterName"] %in% config$report_parameters_offline,] %>% 
              dplyr::mutate_(label = "sprintf('%s (%s)',ParameterName, ParameterUnit)")

    for (i in seq_along(config$report_parameters_offline)) {
      
    sel_par2 <- config$report_parameters_offline[order(config$report_parameters_offline)][i]
      
    n_measurements <- nrow(offline[offline[,"ParameterName"] == sel_par2,])
    
    if (n_measurements > 0) {
    
    g2 <- ggplot2::ggplot(offline, ggplot2::aes_string(x = "DateTime",
                                    y = "ParameterValue",
                                    col = "SiteName")) +
      ggforce::facet_wrap_paginate(~label,
                                   nrow = 1,
                                   ncol = 1,
                                   scales = "free_y",
                                   page = i) +
      ggplot2::geom_point() +
      ggplot2::geom_line() +
      ggplot2::theme_bw(base_size = 20) +
      ggplot2::theme(legend.position = "top" 
                     , strip.text.x = element_text(face = "bold") 
                     , legend.title = element_blank()
                     #, axis.title = element_text(colour="black", size = 20)
                     #, axis.text = element_text(colour="black", size = 20)
                     ) +
      ggplot2::labs(x = "", y = "")
    
    if (config$report_add_thresholds == TRUE & sel_par2 %in% unique(thresholds$ParameterName)) {
     sel_threshold2 <- thresholds[thresholds$ParameterName == sel_par2,]
     g2 <- g2 + ggplot2::geom_hline(yintercept =  sel_threshold2$ParameterThreshold, 
                                   linetype = "dashed")   
     } 
    print(g2) 
    }
    }
```

## Calculated parameters

**You selected the following `r length(config$report_parameters_calculated)` parameter(s) for plotting:**

`r print_items(config$report_parameters_calculated)`

```{r, echo=FALSE, message=FALSE}
calc_paras <- kwb.pilot::calculate_operational_parameters(df = config$report_tz)

idx_selected_paras <- calc_paras$ParameterName %in% config$report_parameters_calculated

plot_calculated_operational_timeseries(calc_paras[idx_selected_paras,])
```

# Correlations

## Flow vs. redox potential difference (outflow - inflow)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
calc_paras <- kwb.pilot::calculate_operational_parameters(df = config$report_tz)

flux <- config$report_tz[config$report_tz$ParameterCode == "Flux", c("DateTime", "ParameterCode", "ParameterValue")]

tmp <- calc_paras %>% 
  dplyr::filter_(~ParameterCode %in% c("Pump_WhPerCbm", "Cell_WhPerCbm", "Redox_Diff")) %>% 
  dplyr::select_("DateTime", "ParameterCode", "ParameterValue") %>% 
  rbind(flux) %>%
  tidyr::spread_(key_col = "ParameterCode", value_col = "ParameterValue") 

plot_correlation <- function(df, 
                 x = "Flux",
                 y = "Redox_Diff", 
                 xlab = "Flow (L/h)",
                 ylab = "Redox potential difference (mV)") {
g <- ggplot2::ggplot(tmp, aes_string(x = x, 
                       y = y)) +
    ggplot2::geom_point() +    # Use hollow circles
    ggplot2::geom_smooth(method = lm) +  # Add linear regression line 
                              #  (by default includes 95% confidence region)
ggplot2::theme_bw(base_size = 17) +
      ggplot2::theme(legend.position = "top" 
                     , strip.text.x = element_text(face = "bold") 
                     , legend.title = element_blank()
                     #, axis.title = element_text(colour="black", size = 20)
                     #, axis.text = element_text(colour="black", size = 20)
                     ) +
      ggplot2::labs(x = xlab, y = ylab)
print(g)
}

plot_correlation(tmp)
```

## Flow vs. specific energy demand of electrolysis cell

```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_correlation(tmp, y = "Cell_WhPerCbm", ylab = "Specific energy demand of cell (Wh/m3)")
```
